Dependently Typed Languages in Statix

### 2022-10-12 paper-evcs/oasics-v2021-sample-article.tex
Add gitignore
Work on paper

\section{Background}

>>>>

\section{Calculus of Constructions}

The base language that was implemented is the Calculus of Constructions \cite{Coquand_Huet_1988}, the language at the top of the lambda cube. One extra feature was added that is not present in the Calculus of Constructions, let bindings.

\subsection{How scope graphs are used}

To type-check the base language, we need to store information about the names we have encountered. There are two different situations, names that we encounter that do not have a known value (only a type), such as function arguments, and names that do have a known value, such as let bindings.

   we need scope graphs. This section describes how scope graphs are used.

The scope graph only has a single type of edge, called \verb|P| (parent) edges. It also only has a single relation, called \verb|name|. This name stores a \verb|NameEntry|, which can be either a \verb|NameType|, which stores the type of a name, or a \verb|NameSubst|, which stores a substitution corresponding to a name.

\begin{lstlisting}
	signature sorts
	NameEntry
	constructors
	NameType : Expr -> NameEntry
	NameSubst : scope * Expr -> NameEntry
	relations
	name : ID -> NameEntry
	name-resolution	labels P
\end{lstlisting}

These are all the definitions we will need to type-check programs. Next, we will introduce some Statix relations that can be used to interact with these scope graphs:

\begin{lstlisting}
	scopePutType : scope * ID * Expr -> scope
	scopePutSubst : scope * ID * (scope * Expr) -> scope
	scopeGetName : scope * ID -> NameEntry
	scopeGetNames : scope * ID -> list((path * (ID * NameEntry)))
	empty_scope : -> scope
\end{lstlisting}

The \verb|scopePutType| and \verb|scopePutSubsts| relations generate a new scope given a parent scope and a type or substitution respectively. To query the scope graph, use \verb|scopeGetName| or \verb|scopeGetNames|, which will return a \verb|NameEntry| or a list of \verb|NameEntries| respectively that the query found. Finally, \verb|empty_scope| returns a fresh empty scope.

System F, which allows a term to depend on a type (also known as Type Polymorphism or Type-Generic Functions)  has been implemented before

The Calculus of Constructions is the top of the lambda cube. System F, which
